---
title: "Go Fund Me Data Analysis"
author: "Matthew Roohan (mlr287), Aishwarya Gupta, Ryun Shim, Helena Xiong"
format: html
editor: visual
---

## Data and packages

We start with loading the packages we'll use.

```{r}
#| label: load-packages
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
```

```{r}
#| label: import-data

gfm_data <- read.csv("~/5306/data/gfm_cleaned_data.csv")
```

## Data Analysis

-   Time analysis:

    -   Are there seasonal variations in campaign success on GoFundMe? Do certain times of the year witness more successful campaigns?

    -   How does the length of the fundraising campaign impact its success? Are longer or shorter campaigns more effective in reaching their funding goals?

```{r}
#| label: time-analysis

#Creating time analysis dataset 
time_analysis <- select(gfm_data, category, position, amount_raised, goal, number_of_donators, campaign_length_days)

#was the goal reached or not? 
time_analysis$goal_reached <- ifelse(time_analysis$amount_raised >=time_analysis$goal, "Yes", "No")

#clean dataset 
time_analysis <- time_analysis[complete.cases(time_analysis$campaign_length_days, time_analysis$goal_reached), ]

#graph analysis
time_analysis$goal_reached <- factor(time_analysis$goal_reached, levels = c("No", "Yes"))

# Create a boxplot to compare campaign lengths for goal reached and not reached campaigns
ggplot(time_analysis, aes(x = goal_reached, y = campaign_length_days, fill = goal_reached)) +
  geom_boxplot() +
  labs(x = "Goal Reached", y = "Campaign Length (Days)",
       title = "Impact of Campaign Length on Goal Achievement") +
  theme_minimal()
```

-   Both Yes and No Goal reached have very similar
