---
title: "Go Fund Me Data Analysis"
author: "Matthew Roohan (mlr287), Aishwarya Gupta (ag2469), Ryun Shim, Helena Xiong"
format: html
editor: visual
---

## Data and packages

We start with loading the packages we'll use.

```{r}
#| label: load-packages
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
library(ggplot2)
```

```{r}
#| label: import-data

gfm_data <- read.csv("data/gfm_cleaned_data.csv")
```

## Data Analysis

-   Time analysis:

    -   How does the length of the fundraising campaign impact its success? Are longer or shorter campaigns more effective in reaching their funding goals?

```{r}
#| label: time-analysis

#Creating time analysis dataset 
time_analysis <- select(gfm_data, category, position, amount_raised, goal, number_of_donators, campaign_length_days)

#was the goal reached or not? 
time_analysis$goal_reached <- ifelse(time_analysis$amount_raised >=time_analysis$goal, "Yes", "No")

#clean dataset 
time_analysis <- time_analysis[complete.cases(time_analysis$campaign_length_days, time_analysis$goal_reached), ]

#graph analysis
time_analysis$goal_reached <- factor(time_analysis$goal_reached, levels = c("No", "Yes"))

# Create a boxplot to compare campaign lengths for goal reached and not reached campaigns
ggplot(time_analysis, aes(x = goal_reached, y = campaign_length_days, fill = goal_reached)) +
  geom_boxplot() +
  labs(x = "Goal Reached", y = "Campaign Length (Days)",
       title = "Impact of Campaign Length on Goal Achievement") +
  theme_minimal()
```

-   Both Yes and No Goal reached have very similar

```{r}

time_analysis$goal_reached <- factor(time_analysis$goal_reached, levels = c("No", "Yes"))

# Aggregate counts for each unique combination of "campaign_length_days" and "goal_reached"
aggregated_data <- aggregate(goal_reached ~ campaign_length_days, data = time_analysis, FUN = table)

# Rename the columns
colnames(aggregated_data) <- c("Campaign_Length_Days", "Counts")

# Split "Counts" column into separate columns for "No" and "Yes"
aggregated_data <- cbind(aggregated_data, as.data.frame(aggregated_data$Counts))

# Remove the original "Counts" column
aggregated_data <- subset(aggregated_data, select = -Counts)

# Rename the columns for "No" and "Yes"
colnames(aggregated_data)[2:3] <- c("No_Count", "Yes_Count")

aggregated_data$yes_probability <- aggregated_data$Yes_Count / (aggregated_data$No_Count + aggregated_data$Yes_Count)

# Print the new dataframe
print(aggregated_data)



# Assuming "aggregated_data" is your dataframe

# Define the ranges for each group of campaign lengths
breaks <- c(0, 7, 14, 21, 30, 60, 90, 120, 150, 180)

# Create a new column for the groups
aggregated_data$weeks <- cut(aggregated_data$Campaign_Length_Days, breaks = breaks, labels = FALSE)

# Aggregate data based on the groups
aggregated_month_data <- aggregate(cbind(No_Count, Yes_Count) ~ weeks, data = aggregated_data, FUN = sum)

aggregated_month_data[5, 1] <- 8
aggregated_month_data[6, 1] <- 12
aggregated_month_data[7, 1] <- 16
aggregated_month_data[8, 1] <- 20
aggregated_month_data[9, 1] <- 24
print(aggregated_month_data)

aggregated_month_data$yes_probability <- aggregated_month_data$Yes_Count / (aggregated_month_data$No_Count + aggregated_month_data$Yes_Count)



# Create a line plot
ggplot(aggregated_month_data, aes(x = weeks, y = yes_probability)) +
  geom_line() +
  scale_x_continuous(breaks = seq(min(aggregated_month_data$weeks), max(aggregated_month_data$weeks), by = 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1), limits = c(0, 1)) +
  labs(x = "Weeks", y = "Goal Reached Probability",
       title = "Goal Reached Probability over Weeks")

```

-   Text Analysis

    -   Can the language used in the title and text of the campaign (such as sentiment, keywords, urgency) be linked to its success? Are there common themes or words in the most successful campaigns?

        ```{r}

        ```

    -   Can sentiment analysis of campaign descriptions provide insights into campaign success on GoFundMe? How do positive or negative sentiments affect donor engagement and fundraising outcomes?"

        ```{r}

        ```
